PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-09-21 main.tex
Fill out more of intro

N body simulations allow us to work back to the planetesimal accretion phase. No one has applied this model to the in situ formation of STIPs yet. Does runaway and oligarchic growth still operate?

>>>>

Over the last few decades, terrestrial planet formation models have largely advanced by matching properties of the solar system. Compared to exoplanetary systems, the solar system provides a rich set of constraints (isotopic ratios, cratering records, small body populations) that are mostly unmeasurable for even the closest neighboring planet forming systems. However, the system architectures discovered by spaced-based missions in the last decade reveal that the solar system could very well be an outlier in terms of what a typical planet-forming disk produces. In addition, the sizes and compositions of the terrestrial planets likely rely on a series of finely-tuned events to play out that involve truncation of the primordial planetesimal disk \citep{raymond17}, inward, followed by outward migration of an outer giant planet \citep{walsh11}, or a large-scale instability triggered by a pair of convergently migrating giant planets \citep{tsiganis05, levison11, nesvorny11}. Given qualitatively similar initial conditions, solar system formation models can even occasionally reproduce the correct masses and orbital periods of the terrestrial planets without invoking any of the aforementioned scenarios, given the right random number seed \citep{fischer14}.

Given the difficult question of whether to treat the solar system as an outlier, the best way forward is to use statistical samples of exoplanetary architectures to develop and inform formation models. This is generally done through the use of population synthesis models (ida + lin, alibert), but many of the mechanisms in these models are informed and tuned by solar system constraints. One pervasive and exotic result revealed by the Kepler space telescope has the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs). Although there is no formal definition of a STIP, they typically contain 3 or more Earth-sized planets with orbital periods extending between 1 and 100 days. Reconciling the structural differences between the solar system (devoid of large bodies interior to 88 days) and STIPs is going to be an important step in building a general, widely-applicable planet formation model.

To date, a large body of work exists that has attempted to reproduce the architectures of STIPs, starting from planetary embryos (cite some examples). However, the runaway and oligarchic growth phases, which precede the assembly of the embryos, are assumed to be ubiquitous. Given that the timescales for accretion and gravitational scattering scale differently with encounter velocity, which itself scales with orbital period, it is not entirely clear that planetary embryos should form in the same way close to the star as they do at much longer, more thoroughly studied orbital periods. In this paper, we use direct N-body simulations to explore the outcome of the planetesimal accretion stage at orbital periods shorter than 100 days. In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
